Flip score characterisation

### 2018-06-29 scripts/3-metric_characterisation/4-edge_flip.Rmd

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(dynalysis)
library(tidyverse)
library(dyneval)
library(cowplot)
```

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(dynbenchmark)
library(tidyverse)
library(dyneval)
library(cowplot)
```
